Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-07-02 text/paper/paper.tex
paper added notes

\citet{ChemlaSpector2010:Experimental-Ev} also took issue with
\citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s design, arguing
that, firstly, the pictorial material used in
\citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s study was unduly
difficult; that, secondly, these pictures also may have failed to make
the local reading sufficiently relevant; and that, thirdly, the
restriction to a categorial choice (whether the sentence fits the
picture of not) may induce a bias against non-preferred readings in
cases where candidate readings stand in entailment relations
\citep[c.f.][for this latter
criticism]{Sauerland2010:Embedded-Implic}. To meet these potential
problems, \citet{ChemlaSpector2010:Experimental-Ev} presented subjects
with pictorial material like that in Figure~\ref{fig:Chemla-Spector},
which was assumed to be easier to assess and better at highlighting
the relevance of the local readings. Additionally, subjects were
asked, not for categorial judgements, but for graded judgements:
subjects could freely click on a scale, as shown in
Figure~\ref{fig:Chemla-Spector}, to indicate how much they considered
a picture fitting for a given sentence \citep[c.f.][for more on this
method]{Chemla2009:Presuppositions}.

@@

Albeit in a different format, the pictures used by
\citeauthor{ChemlaSpector2010:Experimental-Ev} were all different
instantiation of the situation types in
Figures~\ref{fig:AS-distinguishing-pics} and
\ref{fig:ES-distinguishing-pics}. The results reported in this study
are averaged clicking positions, as shown in
Figure~\ref{fig:Chemla-Spector-Results}.
%
\begin{figure}
  \centering
  \subfloat[][\as-condition]{
    \label{fig:CS-Results-as}
        \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_AE.png}
  }
  \subfloat[test][\es-condition]{
    \label{fig:CS-Results-es}
    \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_GE.png}
  }
  \caption{Results from
    \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
    (\citeyear{ChemlaSpector2010:Experimental-Ev}) study}
  \label{fig:Chemla-Spector-Results}
\end{figure}
%
According to \citeauthor{ChemlaSpector2010:Experimental-Ev}, the
crucial piece of evidence for the availability of local readings for
\as-sentences was that these sentences yielded higher graded
acceptability scores for the strong situation than for the weak
situation (although these differ only with respect to the truth value
of the local reading). In a similar way, evidence for the availability
of the local reading for \es-sentences comes from the difference
between the local and the literal situation. Strikingly, in the latter
case, the \es-sentences received an average of 73\% acceptability in
the local situation although the literal and global readings are false
in this case.

@@

We also tested examples like (\ref{bsp:EA}), which are the ``global
alternatives'' to \es-sentences, with a universal quantifier where
\es-sentences have scalar \emph{some}.
\begin{exe}
\ex \gll F\"{u}r \mymark{genau} \mymark{eines} dieser Kinder gilt: es mag \mymark{jede} dieser
  Speisen. \label{bsp:EA}\\
  For exactly one {of these} children {it holds} it likes all {of
    these} dishes.\\
  For exactly one of these children it holds that it likes all of these dishes.
\end{exe}
Sentence like (\ref{bsp:EA}) are literally true in both of the
situations given in Figure~\ref{fig:EA-distinguishing-pics}, but these
situations differ in the truth value of the corresponding
\es-sentence. Interestingly, we found a difference in acceptability,
but a curious one. The sentence was judged \emph{true} in 90.34\% of
the cases for the situation in Figure~\ref{fig:global-EA} and in
98.34\% in situation \ref{fig:literal-EA}. The observed difference is
significant ($t = -3.8259$, $df = 322.375$, $p < 0.001$). That is a
curious finding, because, from the point of view of implicature
calculation, the only thing that could plausibly explain this
acceptability difference is the presence of a global implicature,
resulting from the negation of the corresponding \es-sentence. But
such a putative global implicature would be true in the
situation~\ref{fig:global-EA}, but false in the
situation~\ref{fig:literal-EA}. Consequently, the observed difference
in acceptability cannot be explained simply in terms of the hypothesis
of \citet{ChemlaSpector2010:Experimental-Ev} that acceptability is
proportional to the number of available true readings: if a putative
global reading is at stake, the acceptability pattern should be
reversed; if no such global reading is at stake, then the
acceptability difference cannot be explained.

>>>>

\citet{ChemlaSpector2010:Experimental-Ev} also took issue with
\citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s design, arguing
that, firstly, the pictorial material used in
\citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s study was unduly
difficult; that, secondly, these pictures also may have failed to make
the local reading sufficiently relevant; and that, thirdly, the
restriction to a categorial choice (whether the sentence fits the
picture of not) may induce a bias against non-preferred readings in
cases where candidate readings stand in entailment relations
\citep[c.f.][for this latter
criticism]{Sauerland2010:Embedded-Implic}. To meet these potential
problems, \citet{ChemlaSpector2010:Experimental-Ev} presented subjects
with pictorial material like that in Figure~\ref{fig:Chemla-Spector},
which was assumed to be easier to assess and better at highlighting
the relevance of the local readings. Albeit in a different format, the
pictures used by \citeauthor{ChemlaSpector2010:Experimental-Ev} were
all different instantiation of the situation types in
Figures~\ref{fig:AS-distinguishing-pics} and
\ref{fig:ES-distinguishing-pics}. Additionally, subjects were asked,
not for categorial judgements, but for \mymark{graded judgements}:
subjects could freely click on a scale, as shown in
Figure~\ref{fig:Chemla-Spector}, to indicate how much they considered
a picture fitting for a given sentence \citep[c.f.][for more on this
method]{Chemla2009:Presuppositions}.

@@

\citeauthor{ChemlaSpector2010:Experimental-Ev} hypothesized that the
degree to which a sentence was rated acceptable is proportional to the
number of available true readings. Observed averaged clicking
positions are shown in Figure~\ref{fig:Chemla-Spector-Results}.
%
\begin{figure}
  \centering
  \subfloat[][\as-condition]{
    \label{fig:CS-Results-as}
        \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_AE.png}
  }
  \subfloat[test][\es-condition]{
    \label{fig:CS-Results-es}
    \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_GE.png}
  }
  \caption{Results from
    \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
    (\citeyear{ChemlaSpector2010:Experimental-Ev}) study}
  \label{fig:Chemla-Spector-Results}
\end{figure}
%
According to \citeauthor{ChemlaSpector2010:Experimental-Ev}, the
crucial piece of evidence for the availability of local readings for
\as-sentences was that these sentences yielded higher graded
acceptability scores for the strong situation than for the weak
situation (although these differ only with respect to the truth value
of the local reading). In a similar way, evidence for the availability
of the local reading for \es-sentences comes from the difference
between the local and the literal situation. Strikingly, in the latter
case, the \es-sentences received an average of 73\% acceptability in
the local situation although the literal and global readings are false
in this case.

@@

\begin{center}
  \textbf{Micha's notes:}
\end{center}

\begin{itemize}
\item K1:
  \begin{itemize}
  \item tried to replicate
    \citet{GeurtsPouscoulous2009:Embedded-Implic}'s study
  \item but tested all conditions
  \item used German cleft-sentences (possibly problematic)
  \item some evidence for subjective patterns in answers
  \end{itemize}
\item We also tested examples like (\ref{bsp:EA}), which are the ``global
alternatives'' to \es-sentences, with a universal quantifier where
\es-sentences have scalar \emph{some}.
\begin{exe}
\ex \gll F\"{u}r \mymark{genau} \mymark{eines} dieser Kinder gilt: es
  mag \mymark{jede} dieser Speisen. \label{bsp:EA}\\
  For exactly one {of these} children {it holds} it likes all {of
    these} dishes.\\
  For exactly one of these children it holds that it likes all of these dishes.
\end{exe}
Sentence like (\ref{bsp:EA}) are literally true in both of the
situations given in Figure~\ref{fig:EA-distinguishing-pics}, but these
situations differ in the truth value of the corresponding
\es-sentence. Interestingly, we found a difference in acceptability,
but a curious one. The sentence was judged \emph{true} in 90.34\% of
the cases for the situation in Figure~\ref{fig:global-EA} and in
98.34\% in situation \ref{fig:literal-EA}. The observed difference is
significant ($t = -3.8259$, $df = 322.375$, $p < 0.001$). That is a
curious finding, because, from the point of view of implicature
calculation, the only thing that could plausibly explain this
acceptability difference is the presence of a global implicature,
resulting from the negation of the corresponding \es-sentence. But
such a putative global implicature would be true in the
situation~\ref{fig:global-EA}, but false in the
situation~\ref{fig:literal-EA}. Consequently, the observed difference
in acceptability cannot be explained simply in terms of the hypothesis
of \citet{ChemlaSpector2010:Experimental-Ev} that acceptability is
proportional to the number of available true readings: if a putative
global reading is at stake, the acceptability pattern should be
reversed; if no such global reading is at stake, then the
acceptability difference cannot be explained.
\end{itemize}
